The benefits of an extended feature space in a machine learning bot for the game Schnapsen

### 2018-02-01 Text/paper.tex
Changed things

\begin{center}
\begin{tabular}{| r | r | r | r || r |}
\hline
      & \textbf{rand} & \textbf{bully} & \textbf{rdeep} & \textbf{Total} \\ \hline
      ml\_minimal & -2,65\% & -4,45\% & +35,4\% & \textbf{+1,45\%}   \\ \hline
      ml\_stripped & -15\% & -3,76\% & +10,11\% & \textbf{-6,85\%}  \\ \hline
      ml\_enriched & +1,73\% & -9,01\% & +10,5\% & \textbf{-1,85\%} \\ \hline
      ml\_advanced & -1,15\% & -7,76\% & +13,6\%& \textbf{-2,15\%}  \\ \hline
      ml\_combined & +9,58\% & -13,35\% & +6,61\% & \textbf{-0,85\%}  \\ \hline \hline
      Average improvement & \textbf{-1,5\%} & \textbf{-7,67\%} & \textbf{+15,24\%} &\textbf{-2,05\%} \\ \hline
\end{tabular} \\
\end{center}

@@

\item Game output

\item 
\end{enumerate}
\section{Worksheet III}
\begin{enumerate}
\item The added code:
\begin{lstlisting}[language=bash]
value = self.heuristic(next_state)

>>>>

\begin{center}
\begin{tabular}{| r | r | r | r || r |}
\hline
      & \textbf{rand} & \textbf{bully} & \textbf{rdeep} & \textbf{Total} \\ \hline
      ml\_minimal & -2,65\% & -4,45\% & +35,4\% & \textbf{+1,45\%}   \\ \hline
      ml\_stripped & -15\% & -3,76\% & +10,11\% & \textbf{-6,85\%}  \\ \hline
      ml\_enriched & +1,73\% & -11,87\% & +10,5\% & \textbf{-3,10\%} \\ \hline
      ml\_advanced & -1,15\% & -7,76\% & +13,6\%& \textbf{-2,15\%}  \\ \hline
      ml\_combined & +9,58\% & -13,35\% & +6,61\% & \textbf{-0,85\%}  \\ \hline \hline
      Average improvement & \textbf{-1,5\%} & \textbf{-8,24\%} & \textbf{+15,24\%} &\textbf{-2,3\%} \\ \hline
\end{tabular} \\
\end{center}

@@

\begin{lstlisting}[language=bash]
from kb import KB, Boolean, Integer

# Initialise all variables that you need for you strategies and game knowledge.
# Add those variables here.. The following list is complete for the Play Jack strategy.
J0 = Boolean('j0')
J1 = Boolean('j1')
J2 = Boolean('j2')
J3 = Boolean('j3')
J4 = Boolean('j4')
J5 = Boolean('j5')
J6 = Boolean('j6')
J7 = Boolean('j7')
J8 = Boolean('j8')
J9 = Boolean('j9')
J10 = Boolean('j10')
J11 = Boolean('j11')
J12 = Boolean('j12')
J13 = Boolean('j13')
J14 = Boolean('j14')
J15 = Boolean('j15')
J16 = Boolean('j16')
J17 = Boolean('j17')
J18 = Boolean('j18')
J19 = Boolean('j19')
PJ0 = Boolean('pj0')

Q0 = Boolean('q0')
Q1 = Boolean('q1')
Q2 = Boolean('q2')
Q3 = Boolean('q3')
Q4 = Boolean('q4')
Q5 = Boolean('q5')
Q6 = Boolean('q6')
Q7 = Boolean('q7')
Q8 = Boolean('q8')
Q9 = Boolean('q9')
Q10 = Boolean('q10')
Q11 = Boolean('q11')
Q12 = Boolean('q12')
Q13 = Boolean('q13')
Q14 = Boolean('q14')
Q15 = Boolean('q15')
Q16 = Boolean('q16')
Q17 = Boolean('q17')
Q18 = Boolean('q18')
Q19 = Boolean('q19')

K0 = Boolean('k0')
K1 = Boolean('k1')
K2 = Boolean('k2')
K3 = Boolean('k3')
K4 = Boolean('k4')
K5 = Boolean('k5')
K6 = Boolean('k6')
K7 = Boolean('k7')
K8 = Boolean('k8')
K9 = Boolean('k9')
K10 = Boolean('k10')
K11 = Boolean('k11')
K12 = Boolean('k12')
K13 = Boolean('k13')
K14 = Boolean('k14')
K15 = Boolean('k15')
K16 = Boolean('k16')
K17 = Boolean('k17')
K18 = Boolean('k18')
K19 = Boolean('k19')

PC0 = Boolean('pc0')
PC1 = Boolean('pc1')
PC2 = Boolean('pc2')
PC3 = Boolean('pc3')
PC4 = Boolean('pc4')
PC5 = Boolean('pc5')
PC6 = Boolean('pc6')
PC7 = Boolean('pc7')
PC8 = Boolean('pc8')
PC9 = Boolean('pc9')
PC10 = Boolean('pc10')
PC11 = Boolean('pc11')
PC12 = Boolean('pc12')
PC13 = Boolean('pc13')
PC14 = Boolean('pc14')
PC15 = Boolean('pc15')
PC16 = Boolean('pc16')
PC17 = Boolean('pc17')
PC18 = Boolean('pc18')
PC19 = Boolean('pc19')

def general_information(kb):
    # GENERAL INFORMATION ABOUT THE CARDS
    # This adds information which cards are Jacks
    kb.add_clause(J4)
    kb.add_clause(~Q4)
    kb.add_clause(~K4)
    kb.add_clause(J9)
    kb.add_clause(~Q9)
    kb.add_clause(~K9)
    kb.add_clause(J14)
    kb.add_clause(~Q14)
    kb.add_clause(~K14)
    kb.add_clause(J19)
    kb.add_clause(~Q19)
    kb.add_clause(~K19)
    kb.add_clause(Q3)
    kb.add_clause(~K3)
    kb.add_clause(~J3)
    kb.add_clause(Q8)
    kb.add_clause(~K8)
    kb.add_clause(~J8)
    kb.add_clause(Q13)
    kb.add_clause(~K13)
    kb.add_clause(~J13)
    kb.add_clause(Q18)
    kb.add_clause(~K18)
    kb.add_clause(~J18)
    kb.add_clause(K2)
    kb.add_clause(~Q2)
    kb.add_clause(~J2)
    kb.add_clause(K7)
    kb.add_clause(~Q7)
    kb.add_clause(~J7)
    kb.add_clause(K12)
    kb.add_clause(~Q12)
    kb.add_clause(~J12)
    kb.add_clause(K17)
    kb.add_clause(~Q17)
    kb.add_clause(~J17)
    # Add here whatever is needed for your strategy.

def strategy_knowledge(kb):
    # DEFINITION OF THE STRATEGY
    # Add clauses (This list is sufficient for this strategy)
    # PJ is the strategy to play jacks first, so all we need to model is all x PJ(x) <-> J(x),
    # In other words that the PJ strategy should play a card when it is a jack
    kb.add_clause(~PC4, J4, Q4, K4)
    kb.add_clause(~PC9, J9, Q9, K9)
    kb.add_clause(~PC14, J14, Q14, K14)
    kb.add_clause(~PC19, J14, Q14, K14)

    kb.add_clause(PC4, ~J4, ~Q4, ~K4)
    kb.add_clause(PC9, ~J9, ~Q9, ~K9)
    kb.add_clause(PC14, ~J14, ~Q14, ~K14)
    kb.add_clause(PC19, ~J14, ~Q14, ~K14)

    kb.add_clause(~PC3, J3, Q3, K3)
    kb.add_clause(~PC8, J8, Q8, K8)
    kb.add_clause(~PC13, J13, Q13, K13)
    kb.add_clause(~PC18, J18, Q18, K18)

    kb.add_clause(PC3, ~J3, ~Q3, ~K3)
    kb.add_clause(PC8, ~J3, ~Q3, ~K3)
    kb.add_clause(PC13, ~J13, ~Q13, ~K13)
    kb.add_clause(PC18, ~J18, ~Q18, ~K18)

    kb.add_clause(~PC2, J2, Q2, K2)
    kb.add_clause(~PC7, J7, Q7, K7)
    kb.add_clause(~PC12, J12, Q12, K12)
    kb.add_clause(~PC17, J17, Q17, K17)

    kb.add_clause(PC2, ~J2, ~Q2, ~K2)
    kb.add_clause(PC7, ~J7, ~Q7, ~K7)
    kb.add_clause(PC12, ~J12, ~Q12, ~K12)
    kb.add_clause(PC17, ~J17, ~Q17, ~K17)

8. Game output:
   Start state: The game is in phase: 1
Player 1's points: 0, pending: 0
Player 2's points: 0, pending: 0
The trump suit is: C
Player 1's hand: AC KD QD QS JS
Player 2's hand: 10C QC JC 10H JH
There are 10 cards in the stock

player1: <bots.kbbot.kbbot.Bot instance at 0x102a72290>
player2: <bots.rand.rand.Bot instance at 0x102a72518>
*   Player 2 plays: JC
The game is in phase: 1
Player 1's points: 0, pending: 0
Player 2's points: 0, pending: 0
The trump suit is: C
Player 1's hand: AC KD QD QS JS
Player 2's hand: 10C QC JC 10H JH
There are 10 cards in the stock
Player 2 has played card: J of C

*   Player 1 plays: JS
The game is in phase: 1
Player 1's points: 0, pending: 0
Player 2's points: 4, pending: 0
The trump suit is: C
Player 1's hand: AC KD QD AS QS
Player 2's hand: 10C QC 10H QH JH
There are 8 cards in the stock

*   Player 2 plays: QH
The game is in phase: 1
Player 1's points: 0, pending: 0
Player 2's points: 4, pending: 0
The trump suit is: C
Player 1's hand: AC KD QD AS QS
Player 2's hand: 10C QC 10H QH JH
There are 8 cards in the stock
Player 2 has played card: Q of H

*   Player 1 plays: KD
The game is in phase: 1
Player 1's points: 0, pending: 0
Player 2's points: 11, pending: 0
The trump suit is: C
Player 1's hand: AC QD KH AS QS
Player 2's hand: 10C QC 10H JH 10S
There are 6 cards in the stock

*   Player 2 plays: JH
The game is in phase: 1
Player 1's points: 0, pending: 0
Player 2's points: 11, pending: 0
The trump suit is: C
Player 1's hand: AC QD KH AS QS
Player 2's hand: 10C QC 10H JH 10S
There are 6 cards in the stock
Player 2 has played card: J of H

*   Player 1 plays: AS
The game is in phase: 1
Player 1's points: 0, pending: 0
Player 2's points: 24, pending: 0
The trump suit is: C
Player 1's hand: AC QD KH KS QS
Player 2's hand: 10C QC JD 10H 10S
There are 4 cards in the stock

*   Player 2 plays: QC
The game is in phase: 1
Player 1's points: 0, pending: 0
Player 2's points: 24, pending: 0
The trump suit is: C
Player 1's hand: AC QD KH KS QS
Player 2's hand: 10C QC JD 10H 10S
There are 4 cards in the stock
Player 2 has played card: Q of C

*   Player 1 plays: QD
The game is in phase: 1
Player 1's points: 0, pending: 0
Player 2's points: 30, pending: 0
The trump suit is: C
Player 1's hand: AC 10D KH KS QS
Player 2's hand: 10C AD JD 10H 10S
There are 2 cards in the stock

*   Player 2 plays: 10C
The game is in phase: 1
Player 1's points: 0, pending: 0
Player 2's points: 30, pending: 0
The trump suit is: C
Player 1's hand: AC 10D KH KS QS
Player 2's hand: 10C AD JD 10H 10S
There are 2 cards in the stock
Player 2 has played card: 10 of C

*   Player 1 plays: KH
The game is in phase: 2
Player 1's points: 0, pending: 0
Player 2's points: 44, pending: 0
The trump suit is: C
Player 1's hand: AC KC 10D KS QS
Player 2's hand: AD JD AH 10H 10S
There are 0 cards in the stock

*   Player 2 plays: 10S
The game is in phase: 2
Player 1's points: 0, pending: 0
Player 2's points: 44, pending: 0
The trump suit is: C
Player 1's hand: AC KC 10D KS QS
Player 2's hand: AD JD AH 10H 10S
There are 0 cards in the stock
Player 2 has played card: 10 of S

*   Player 1 plays: QS
The game is in phase: 2
Player 1's points: 0, pending: 0
Player 2's points: 57, pending: 0
The trump suit is: C
Player 1's hand: AC KC 10D KS
Player 2's hand: AD JD AH 10H
There are 0 cards in the stock

*   Player 2 plays: JD
The game is in phase: 2
Player 1's points: 0, pending: 0
Player 2's points: 57, pending: 0
The trump suit is: C
Player 1's hand: AC KC 10D KS
Player 2's hand: AD JD AH 10H
There are 0 cards in the stock
Player 2 has played card: J of D

*   Player 1 plays: 10D
The game is in phase: 2
Player 1's points: 12, pending: 0
Player 2's points: 57, pending: 0
The trump suit is: C
Player 1's hand: AC KC KS
Player 2's hand: AD AH 10H
There are 0 cards in the stock

*   Player 1 plays: KS
The game is in phase: 2
Player 1's points: 12, pending: 0
Player 2's points: 57, pending: 0
The trump suit is: C
Player 1's hand: AC KC KS
Player 2's hand: AD AH 10H
There are 0 cards in the stock
Player 1 has played card: K of S

*   Player 2 plays: AD
The game is in phase: 2
Player 1's points: 27, pending: 0
Player 2's points: 57, pending: 0
The trump suit is: C
Player 1's hand: AC KC
Player 2's hand: AH 10H
There are 0 cards in the stock

*   Player 1 plays: AC
The game is in phase: 2
Player 1's points: 27, pending: 0
Player 2's points: 57, pending: 0
The trump suit is: C
Player 1's hand: AC KC
Player 2's hand: AH 10H
There are 0 cards in the stock
Player 1 has played card: A of C

*   Player 2 plays: AH
The game is in phase: 2
Player 1's points: 49, pending: 0
Player 2's points: 57, pending: 0
The trump suit is: C
Player 1's hand: KC
Player 2's hand: 10H
There are 0 cards in the stock

*   Player 1 plays: KC
The game is in phase: 2
Player 1's points: 49, pending: 0
Player 2's points: 57, pending: 0
The trump suit is: C
Player 1's hand: KC
Player 2's hand: 10H
There are 0 cards in the stock
Player 1 has played card: K of C

*   Player 2 plays: 10H
The game is in phase: 2
Player 1's points: 66, pending: 0
Player 2's points: 57, pending: 0
The trump suit is: C
Player 1's hand:
Player 2's hand:
There are 0 cards in the stock

Game finished. Player 1 has won, receiving 1 points.
\end{lstlisting}
\end{enumerate}
\section{Worksheet III}
\begin{enumerate}
\item The added code:
\begin{lstlisting}[language=bash]
value = self.heuristic(next_state)
